# Description

The following Baysian regression implementation is based on Metropolis-Hasting random walk algorithm from Chapter 5 - Applied Bayesian econometrics for Central Bankers. The posterior results are summarized from 1,100,000 iterations with the first 100,000 iterations discarded for each model.


# REGRESSION RESULTS


```{=latex}
		\begin{table}[H]
			\begin{threeparttable}
				\caption {\label{tab:table1} Parameters description}
				%\rowcolors{2}{gray!10}{white} 
				\begin{tabular}{@{}ll@{}}
					\toprule
					Description & Parameter\\
					\midrule
					Log-likelihood value & $llv$ \\[2pt] 
					Credit to household & \\
					\quad Credit to household 1st AR parameter  & $\phi^1_{y}$ \\[2pt] 
					\quad Credit to household 2nd AR parameter  & $\phi^2_{y}$ \\[2pt] 
					\quad Credit to household 1st cross cycle AR parameter  & $\phi^{x1}_{y}$ \\[2pt] 
					\quad Credit to household 2nd cross cycle AR parameter  & $\phi^{x2}_{y}$ \\[2pt] 
					\quad S.D. of permanent shocks to Credit to household & $\sigma_{ny}$ \\[2pt] 
					\quad S.D. of transitory shocks to Credit to household & $\sigma_{ey}$ \\[2pt]
					Housing Price Index & \\
					\quad Housing Price Index 1st AR parameter  & $\phi^1_{h}$ \\[2pt] 
					\quad Housing Price Index 2nd AR parameter  & $\phi^2_{h}$ \\[2pt] 
					\quad Housing Price Index 1st cross cycle AR parameter  & $\phi^{x1}_{h}$ \\[2pt] 
					\quad Housing Price Index 2nd cross cycle AR parameter  & $\phi^{x2}_{h}$ \\[2pt] 
					\quad S.D. of permanent shocks to Housing Price Index & $\sigma_{nh}$ \\[2pt] 
					\quad S.D. of transitory shocks to Housing Price Index & $\sigma_{eh}$ \\[2pt]
					Cross-series correlations & \\
					\quad Correlation: Permanent credit to household/Permanent Housing Price Index  & $\sigma_{nynh}$ \\[2pt] 
					\quad Correlation: Transitory credit to household/Transitory Housing Price Index  & $\sigma_{eyeh}$ \\[2pt] 
										
					\bottomrule
				\end{tabular}
%				\begin{tablenotes}
%					\small
%					\item $y_t$ is credit to household series, $h_t$ is housing price index series. Both are log transformed. \\
%				\end{tablenotes}
			\end{threeparttable}
		\end{table}
```

```{r, echo=FALSE, message=FALSE}
options(kableExtra.latex.load_packages = FALSE)
options(knitr.table.format = "pandoc")
library('kableExtra')
library(dplyr)
library(knitr)

country='GB'
# filepath=sprintf('../../Regression/RegComb_%s.csv',country)
# df<-read.csv(filepath, sep = ",", header=FALSE)		
# 
# rownames(df) <- df[,1]
# df<-df[,-1]
# colnames(df) <- c("Median", "SD", "Median", "SD", "Median", "SD")
# colnamedf<-c("Median", "SD", "Median", "SD", "Median", "SD")
# options(knitr.kable.NA = '')
# 
# 
# kbl(df, "latex", booktabs = T, digits = c(4, 4, 4, 4, 4, 4), caption ='UK Regression Results', escape=FALSE, linesep=c("", "", "", "\\addlinespace")) %>%
#   kable_classic("striped") %>%
#   add_header_above(c("Parameters" = 1, "VAR2" = 2, "VAR2 1-cross lag" = 2, "VAR2 2-cross lags" = 2)) #%>%
#   #footnote(general="UK Bayesian regression results") %>%
#   #kable_styling(latex_options="scale_down")



filepath=sprintf('../../Regression/RegCombPercentile_%s.csv',country)
df<-read.csv(filepath, sep = ",", header=FALSE)

rownames(df) <- df[,1]
df<-df[,-1]
colnames(df) <- c("Median", "10pct", "90pct", "Median", "10pct", "90pct", "Median", "10pct", "90pct")

options(knitr.kable.NA = '')

#df = df %>% mutate_if(is.numeric, format, digits=4)

#kbl(data.frame(x=rnorm(10), y=rnorm(10), x= rnorm(10)), digits = c(1, 4, 4))

kbl(df, "latex", booktabs = T, digits = c(4, 4, 4, 4, 4, 4, 4, 4, 4), caption ='UK Regression Results', escape=FALSE, linesep=c("", "", "", "\\addlinespace")) %>%
  kable_paper("striped") %>%
  add_header_above(c("Parameters" = 1, "VAR2" = 3, "VAR2 1-cross lag" = 3, "VAR2 2-cross lags" = 3)) %>%
  footnote(general="UK Bayesian regression results") %>%
  kable_styling(latex_options="scale_down") %>%
  column_spec(5:7, bold = c(0,0,1,0,0,0,1,0,0,0,0,0,0,0,0))
```		

\clearpage


```{r, echo=FALSE, message=FALSE}
options(kableExtra.latex.load_packages = FALSE)
options(knitr.table.format = "pandoc")
library('kableExtra')
library(dplyr)
library(knitr)

country='US'
# filepath=sprintf('../../Regression/RegComb_%s.csv',country)
# df<-read.csv(filepath, sep = ",", header=FALSE)		
# 
# rownames(df) <- df[,1]
# df<-df[,-1]
# colnames(df) <- c("Median", "SD", "Median", "SD", "Median", "SD")
# colnamedf<-c("Median", "SD", "Median", "SD", "Median", "SD")
# options(knitr.kable.NA = '')
# 
# #df = df %>% mutate_if(is.numeric, format, digits=4)
# 
# #kbl(data.frame(x=rnorm(10), y=rnorm(10), x= rnorm(10)), digits = c(1, 4, 4))
# 
# kbl(df, "latex", booktabs = T, digits = c(4, 4, 4, 4, 4, 4), caption ='US Regression Results', escape=FALSE, linesep=c("", "", "", "\\addlinespace")) %>%
#   kable_classic("striped") %>%
#   add_header_above(c("Parameters" = 1, "VAR2" = 2, "VAR2 1-cross lag" = 2, "VAR2 2-cross lags" = 2)) #%>%
#   #footnote(general="US Bayesian regression results") %>%
#   #kable_styling(latex_options="scale_down")


filepath=sprintf('../../Regression/RegCombPercentile_%s.csv',country)
df<-read.csv(filepath, sep = ",", header=FALSE)

rownames(df) <- df[,1]
df<-df[,-1]
colnames(df) <- c("Median", "10pct", "90pct", "Median", "10pct", "90pct", "Median", "10pct", "90pct")

options(knitr.kable.NA = '')

#df = df %>% mutate_if(is.numeric, format, digits=4)

#kbl(data.frame(x=rnorm(10), y=rnorm(10), x= rnorm(10)), digits = c(1, 4, 4))

kbl(df, "latex", digits = c(4, 4, 4, 4, 4, 4, 4, 4, 4), booktabs = T, caption ='US Regression Results', escape=FALSE, linesep=c("", "", "", "\\addlinespace")) %>%
  kable_paper("striped") %>%
  add_header_above(c("Parameters" = 1, "VAR2" = 3, "VAR2 1-cross lag" = 3, "VAR2 2-cross lags" = 3)) %>%
  footnote(general="US Bayesian regression results") %>%
  kable_styling(latex_options="scale_down") %>%
  column_spec(5:7, bold = c(0,0,1,0,0,0,1,0,0,0,0,0,0,0,0))
```		

\clearpage

# Trend-Cycle Decompositon Graphs
## UK graphs
```{r, echo=FALSE, out.width='85%',  fig.align='center', fig.cap = 'UK VAR(2)'}
knitr::include_graphics('../../Regression/Bayesian_UC_VAR2_nodrift/OutputData/cycles_GB.pdf')
```

```{r, echo=FALSE, out.width='85%',  fig.align='center', fig.cap = 'UK VAR(2) 1 cross-lag'}
knitr::include_graphics('../../Regression/Bayesian_UC_VAR2_nodrift_Crosscycle1lag/OutputData/cycles_GB.pdf')
```

```{r, echo=FALSE, out.width='85%',  fig.align='center', fig.cap = 'UK VAR(2) 2 cross-lags'}
knitr::include_graphics('../../Regression/Bayesian_UC_VAR2_nodrift_Crosscycle2lags/OutputData/cycles_GB.pdf')
```

\clearpage


## US graphs
```{r, echo=FALSE, out.width='85%',  fig.align='center', fig.cap = 'US VAR(2)'}
knitr::include_graphics('../../Regression/Bayesian_UC_VAR2_nodrift/OutputData/cycles_US.pdf')
```

```{r, echo=FALSE, out.width='85%',  fig.align='center', fig.cap = 'US VAR(2) 1 cross-lag'}
knitr::include_graphics('../../Regression/Bayesian_UC_VAR2_nodrift_Crosscycle1lag/OutputData/cycles_US.pdf')
```

```{r, echo=FALSE, out.width='85%',  fig.align='center', fig.cap = 'US VAR(2) 2 cross-lags'}
knitr::include_graphics('../../Regression/Bayesian_UC_VAR2_nodrift_Crosscycle2lags/OutputData/cycles_US.pdf')
```

\clearpage



# Posterior and Prior Distribution
## UK Posterior and Prior Distribution
```{r, echo=FALSE, out.width='85%',  fig.align='center', fig.cap = 'UK VAR(2)'}
knitr::include_graphics('../../Regression/Bayesian_UC_VAR2_nodrift/OutputData/posteriorpriordistribution_GB.pdf')
```

```{r, echo=FALSE, out.width='85%',  fig.align='center', fig.cap = 'UK VAR(2) 1 cross-lag'}
knitr::include_graphics('../../Regression/Bayesian_UC_VAR2_nodrift_Crosscycle1lag/OutputData/posteriorpriordistribution_GB.pdf')
```

```{r, echo=FALSE, out.width='85%',  fig.align='center', fig.cap = 'UK VAR(2) 2 cross-lags'}
knitr::include_graphics('../../Regression/Bayesian_UC_VAR2_nodrift_Crosscycle2lags/OutputData/posteriorpriordistribution_GB.pdf')
```

\clearpage


## US Posterior and Prior Distribution
```{r, echo=FALSE, out.width='85%',  fig.align='center', fig.cap = 'US VAR(2)'}
knitr::include_graphics('../../Regression/Bayesian_UC_VAR2_nodrift/OutputData/posteriorpriordistribution_US.pdf')
```

```{r, echo=FALSE, out.width='85%',  fig.align='center', fig.cap = 'US VAR(2) 1 cross-lag'}
knitr::include_graphics('../../Regression/Bayesian_UC_VAR2_nodrift_Crosscycle1lag/OutputData/posteriorpriordistribution_US.pdf')
```

```{r, echo=FALSE, out.width='85%',  fig.align='center', fig.cap = 'US VAR(2) 2 cross-lags'}
knitr::include_graphics('../../Regression/Bayesian_UC_VAR2_nodrift_Crosscycle2lags/OutputData/posteriorpriordistribution_US.pdf')
```


\clearpage

# Posterior chain

## UK Posterior chain
```{r, echo=FALSE, out.width='85%',  fig.align='center', fig.cap = 'UK VAR(2)'}
knitr::include_graphics('../../Regression/Bayesian_UC_VAR2_nodrift/OutputData/posteriorchain_GB.pdf')
```

```{r, echo=FALSE, out.width='85%',  fig.align='center', fig.cap = 'UK VAR(2) 1 cross-lag'}
knitr::include_graphics('../../Regression/Bayesian_UC_VAR2_nodrift_Crosscycle1lag/OutputData/posteriorchain_GB.pdf')
```

```{r, echo=FALSE, out.width='85%',  fig.align='center', fig.cap = 'UK VAR(2) 2 cross-lags'}
knitr::include_graphics('../../Regression/Bayesian_UC_VAR2_nodrift_Crosscycle2lags/OutputData/posteriorchain_GB.pdf')
```

\clearpage

## US Posterior chain
```{r, echo=FALSE, out.width='85%',  fig.align='center', fig.cap = 'US VAR(2)'}
knitr::include_graphics('../../Regression/Bayesian_UC_VAR2_nodrift/OutputData/posteriorchain_US.pdf')
```

```{r, echo=FALSE, out.width='85%',  fig.align='center', fig.cap = 'US VAR(2) 1 cross-lag'}
knitr::include_graphics('../../Regression/Bayesian_UC_VAR2_nodrift_Crosscycle1lag/OutputData/posteriorchain_US.pdf')
```

```{r, echo=FALSE, out.width='85%',  fig.align='center', fig.cap = 'US VAR(2) 2 cross-lags'}
knitr::include_graphics('../../Regression/Bayesian_UC_VAR2_nodrift_Crosscycle2lags/OutputData/posteriorchain_US.pdf')
```
